Synthesizing Quotient Lenses

### 2018-03-14 papers/QuotientLenses/main.tex
Added Conclusion

\section{Conclusion}
\bcp{And future work!}  \saz{I'm lukewarm about including a description of
future work.  Unless there are specific conjectures or open problems that
are worth mentioning, I'm not sure that it's really that important.}
\bcp{Agreed. But don't we have any ideas for how to extend or generalize or
things to do next or additional questions to consider??  E.g.: 
\begin{itemize}
\item is it easy to extend all this to
asymmetric and symmetric lenses?  (If so, we should say so!)
\item What properties do the bijective lens combinators have to have in
order to validate the normalization property?  (I.e., if we tried to extend
Boomerang's bijective lens combinators with another one, what would happen?)
\item Do we have more ideas for QRE primitives?
\item Etc.
\end{itemize}
}
\label{concl}

>>>>

\section{Conclusion}
In this paper, we showed how to synthesize a class of bijective quotient lenses
using the bijective lens synthesis system Optician as a plug-in for our
synthesis algorithm. In order to achieve this, we first introduced {\em
Quotient regular languages} to specify regular languages with an equivalence
relation defined on them. Then, we introduced {\em QRE lenses}, which
are bijective quotient lenses that map between QREs via bijective lenses. We
proved a normal form theorem for QREs that enabled us to (1) extend the
synthesis algorithm used by Optician to synthesize QRE lenses, and (2) prove
that if there is a QRE lens that satisfies the input specification, then the
extended algorithm returns such a lens. Finally we tested QRE-enhanced optician
on the Optician benchmark suite and demonstrated that QREs can save programmers
significant effort compared to both Optician and basic Boomerang, and that
QRE-enhanced Optician maintains competitive performance over both of these
systems.
\bcp{And future work!}  \saz{I'm lukewarm about including a description of
future work.  Unless there are specific conjectures or open problems that
are worth mentioning, I'm not sure that it's really that important.}
\bcp{Agreed. But don't we have any ideas for how to extend or generalize or
things to do next or additional questions to consider??  E.g.: 
\begin{itemize}
\item is it easy to extend all this to
asymmetric and symmetric lenses?  (If so, we should say so!)
\item What properties do the bijective lens combinators have to have in
order to validate the normalization property?  (I.e., if we tried to extend
Boomerang's bijective lens combinators with another one, what would happen?)
\item Do we have more ideas for QRE primitives?
\item Etc.
\end{itemize}
}
\label{concl}
